Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-25 tex/scam/paper-submit.tex
false positive edit
mods for aos submission

\input{macros}

@@

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John}
  \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{Machine Learning Department, Carnegie Mellon University,
  Pittsburgh PA 15213}
\address{Department of Statistics, University of Chicago, Chicago IL 60637}
\end{aug}

@@

\maketitle
\vskip10pt

@@

\bibliographystyle{imsart-nameyear}
\bibliography{local}

>>>>

\input{macros}
\arxiv{1411.1805}

@@

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu${}^*$}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen${}^\dag$}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John}
  \snm{Lafferty${}^\dag$}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{${}^*$Machine Learning Department, Carnegie Mellon University,
  Pittsburgh PA 15213}
\address{${}^\dag$Department of Statistics, University of Chicago, Chicago IL 60637}
\end{aug}

@@

\maketitle

\vskip10pt

@@

\clearpage
\bibliographystyle{imsart-nameyear}
\bibliography{local}
